Ribosome accumulation during early phase resistance training in humans

### 2021-12-13 manuscript.Rmd
sorted files and added manual edits

read_excel("./data/tr010_age_participant.xlsx") %>%
  inner_join(dxa_whole) %>%
  mutate(age = difftime(recruited, dob)/365.2425, 
         bmi = weight/(height/100)^2) %>%
  dplyr::select(participant, group, height, weight,age, sex,bmi, fat_rel) %>%

>>>>

read_excel("./data/tr010_age_participant.xlsx") %>%
  inner_join(dxa_whole) %>%
  mutate(age = age, 
         bmi = weight/(height/100)^2) %>%
  dplyr::select(participant, group, height, weight,age, sex,bmi, fat_rel) %>%
